Dynamical modeling of tidal streams

### 2013-12-26 tex/ms.tex
streams: mention that we model leading and trailing separately, sign for leading/trailing, some more tweaks

I illustrate the theoretical considerations set forth in this paper by
using a simulated tidal stream. This stream is set up similarly to
that used in \citep{Sanders13b}. The stream is constructed by running
an $N$-body simulation of a King cluster on an orbit similar to that
of the GD-1 stream \citep{Koposov10a}. Specifically, a King cluster
with a mass of $2\times10^4\msun$, a tidal radius of $0.07\kpc$, and a
ratio of the central potential to the velocity dispersion squared of
$2.0$ is sampled using $10^4$ particles. The cluster is evolved in an
external logarithmic host potential with $V_c = 220\kms$ and a
flattening $q=0.9$ ($\Phi = V_c^2 \ln (R^2 + z^2/q^2)$) using the
gyrfalcon code \citep{Dehnen00a,Dehnen02a} with a softening of
$1.5\pc$ in the NEMO toolkit \citep{Teuben95a}. The cluster is evolved
for $5.011\Gyr$ ($=5.125\kpc/[\kms]$) from the initial condition
$(X,Y,Z) = (-11.63337239,-20.76235661,-10.631736273934635)\kpc$ and
$(V_X,V_Y,V_Z) = (-128.8281653,42.88727925,79.172383882274971)\kms$,
chosen such that the cluster ends up at roughly the observed location
of the GD-1 stream at the end of the simulation
\citep{Koposov10a}. The progenitor's orbit has an eccentricity of
$0.31$, a pericenter of $13.7\kpc$, a current $r=14.4\kpc$, such that
the cluster is close to pericenter at the end of the simulation. The
actions of the progenitor are $(J_R,L_Z,J_Z) =
(288.5,-3173.7,897.6)\kpc\kms$ and its orbital frequencies are
$(\Omega_R,\Omega_\phi,\Omega_Z) = (15.7,-10.8,11.9)\Gyr\inv$.

@@

The action and frequency distributions shown in
\figurename~\ref{fig:gd1_jt} combined with the knowledge that for
\emph{any} tidal stream the Hessian $(\partial^2 H / \partial \vecj
\partial \vecj)\large|_{\vecj^p}$ must be strongly dominated by a
single large eigenvalue leads us to propose that frequency--angle
space is a better coordinate system than action--angle space for
modeling tidal streams. That is, the distribution of actions in a
tidal stream has a complicated structure that is hard to capture using
a simple, analytic form (see also the discussion in
\citealt{Eyre11a}). Especially the ``bowtie'' structure in $(J_R,L_Z)$
and the overlapping leading- and trailing-arm distributions in
($J_R,J_Z$) are hard to model with a simple distribution function. The
distribution of frequencies, however, is close-to one dimensional, its
direction of largest variance can be well-modeled as a Gaussian
(although below we will model it slightly differently), and its
parameters can all be easily estimated from the velocity dispersion of
the progenitor, the orbit of the progenitor, and the gravitational
potential, as discussed below. Therefore, we will model tidal streams
in frequency--angle space.

@@

The distribution of frequencies is three dimensional. A general
description in terms of a Gaussian distribution would have nine free
parameters. However, we can model it with fewer free parameters as
follows. First, following \citet{Eyre11a}, we approximate the
\emph{action} distribution as a Gaussian with standard deviations
\begin{equation}
  \sigma_{J_R} = \frac{1}{\pi}\,\sigv\,\left(r_{\mathrm{apo}}-r_{\mathrm{peri}}\right)\,,\quad 
  \sigma_{L_Z} = \sigv\,r_{\mathrm{peri}}\,,\quad 
  \sigma_{J_Z} = \frac{2}{\pi}\,\sigv\,Z_{\mathrm{max}}\,,
\end{equation}
where $\sigv$ is the velocity dispersion of the progenitor,
$r_{\mathrm{apo}}$ and $r_{\mathrm{peri}}$ are the apo- and pericenter
radii of the progenitor orbit, respectively, and $Z_{\mathrm{max}}$ is
the maximum $Z$ reached on this orbit. We assume that the all
correlations between the actions are zero (see
\figurename~\ref{fig:gd1_jt}). Then we propagate this Gaussian
variance to frequency space using the Hessian $(\partial^2 H /
\partial \vecj \partial \vecj)\large|_{\vecj^p}$\footnote{The Hessian
  $(\partial^2 H / \partial \vecj \partial \vecj)\large|_{\vecj^p}$
  can be computed using the method in \appendixname~\ref{sec:aa} by
  computing $\partial (\vecj,\veca) / \partial (\vecx,\vecv)$ and
  $\partial (\veco,\veca) / \partial (\vecx,\vecv)$ and forming
  $\partial \veco / \partial \vecj = \left(\partial (\vecj,\veca) /
  \partial (\vecx,\vecv)\right)^{-1}\,\left(\partial (\veco,\veca) /
  \partial (\vecx,\vecv)\right)$.}, which gives the variance matrix
$V_\veco$. The principal eigenvector of this matrix is the model
direction along which the stream spreads. While the model I propose
here is a simple one, it works well without having been tweaked for
the simulation under scrutiny. The angle between the principal
eigenvector of $V_\veco$ and the progenitor's frequency vector is
$0.50^\circ$ while the value measured from the simulation is
$0.18^\circ$. For a model with an isotropic action distribution, the
misalignment would be $1.28^circ$.

We then further constrain the mean frequency offset to lie along the
principal eigenvector of $V_\veco$. This mean frequency offset can be
described in terms of a parameter $\mu_\Omega = \Delta \Omega^m /
\sigma_{\Omega,1}$, where $\sigma_{\Omega,1}$ is the square root of the
largest eigenvalue of $V_\veco$ and $\Delta \Omega^m$ is the mean
frequency offset. \figurename~\ref{fig:gd1_dohist} shows the
distribution frequency offsets in the direction of the median
frequency offset in the stream. The dashed line is a Gaussian fit to
this distribution, while the solid line is a fit of the form
\begin{equation}\label{eq:do}
  p(|\Delta \veco|_\parallel) = |\Delta \veco|_\parallel\,\mathcal{N}\left(|\Delta \veco|_\parallel|\Delta \Omega^m,\sigma_{\Omega,1}^2\right)\,,
\end{equation}
where $\mathcal{N}(\cdot|\cdot,\cdot)$ represents a Gaussian
distribution. The fit is equally good (because the dispersion is much
smaller than the mean) and we choose the second form because it
simplifies some of the stream-track calculations below. The best-fit
$(\Delta \Omega^m,\sigma_{\Omega,1})$ is $(0.19,0.033)\Gyr\inv$ in
both cases. Based on this information, a model with $\sigv =
0.365\kms$ and $\mu_\Omega = 6$ provides a good fit to the simulation
data. The distribution of frequency offsets in the two-dimensional
space perpendicular to the principal eigenvector of $V_\veco$ is
modeled as a zero-mean Gaussian with variance matrix given by the
projection of $V_\veco$ onto this space.

@@

The discussions of the dynamics of stream formation in the previous
section directly give rise of a generative model of a tidal stream. A
star in a tidal stream is \emph{generated} through being stripped a
time $\Delta t$ ago from a progenitor $(\vecx^p,\vecv^p) \equiv
(\vecj^p,\veca^p)$ by receiving a small offset $(\Delta \vecx,\Delta
\vecv) \equiv (\Delta \vecj,\Delta \veca)$. The offset then evolves
using the dynamical equations given in the previous section and the
star is observed at time $t=0$ (\ie, today). Because phase-space
density is conserved by Liousville's theorem, a probabilistic model
results by relating the likelihood $p(\vecx,\vecv|\vecp)$ (where
$\vecp$ denotes the set of all model parameters; see below) for the
observed phase-space position today to the distribution of initial
offsets. This probabilistic model can be marginalized over missing
observational data or extended to include a model for outliers.

\subsection{Real--space modeling}

In more detail, in the real--space approach the model can be specified
by: (a) the gravitational potential $\Phi$, (b) the current
phase-space position of the progenitor $(\vecx_p,\vecv_p)(t=0)$, which
can be integrated backwards in time by reversing the Hamiltonian flow
defined by $\Phi$, (c) the time $\Delta t_i$ at which each star was
removed from the progenitor, and (d) the distribution $f(\Delta
\vecx,\Delta \vecv|\paramsdiff)$, characterized by some parameters
$\paramsdiff$, of initial phase-space offsets from which the actual
offsets $(\Delta \vecx_i,\Delta \vecv_i)$ are drawn. In practice, $f$
can be taken to be a Gaussian, characterized by a width in position
$\sigma_x$ and in velocity $\sigma_v$, related to the tidal radius and
escape velocity of the progenitor, respectively. However, more
complicated models for the initial phase-space distribution of the
debris can be used here as well.

The time $\Delta t_i$ at which a star was removed is unobservable and
the probability in \eqnname~(\ref{eq:realdft}) should therefore be
integrated over this time using a prior $p(\Delta t_i|\ldots)$, where
$\ldots$ indicates that this prior could depend on other factors such
as the potential and the progenitor orbit\footnote{For example, one
  could insist that stars are removed around pericenter
  passages.}. For simplicity, we can assume a uniform prior for the
times $\Delta t$. The probability for a single star then becomes
\begin{align}\label{eq:realdf}
  p(\vecx_i,\vecv_i | \Phi,\vecx_p,\vecv_p,\paramsdiff) & = \int \dd
  \Delta t_i \,p(\vecx_i,\vecv_i | \Phi,\vecx_p,\vecv_p,\Delta t_i,
  \paramsdiff)\,.
\end{align}
If the progenitor's current phase-space position is unknown, then this
probability should be further marginalized over $(\vecx_p,\vecv_p)$;
for multiple stars, this marginalization is done after multiplying the
individual-star likelihoods in \eqnname~(\ref{eq:realdf}).

In practice, the likelihood in \eqnname~(\ref{eq:realdf}) can be
calculated as follows: for a given potential $\Phi$ and progenitor
$(\vecx_p,\vecv_p)$, we (a) integrate the orbits of all stars
$(\vecx_i,\vecv_i)$ and (b) that of the progenitor backward in time for
many Gyr and record the phase-space positions over time on a grid $j$
in $\Delta^j_i$; (c) we evaluate $f(\Delta \vecx_i,\Delta
\vecv_i)(\Delta t^j_i)$ for all stars $i$ and times $j$; (d) $f(\Delta
\vecx_i,\Delta \vecv_i)(\Delta t^j_i)$ is then summed over $j$ and the
logarithm of that is summed over $i$. The most computationally
expensive part of this calculation is the integration of the various
orbits. The evaluation of the likelihood for different parameters
\paramsdiff\ of $f$ can be efficiently computed by caching the orbit
integrations of (a) and (b); different progenitor orbits
$(\vecx_p,\vecv_p)$ can also make use of the stored orbits in (a).

The approach outlined in this section is straightforward, but very
computationally expensive, as it requires large numbers of orbit
integrations to explore all plausible removal times $\Delta t$,
progenitor orbits, and potentials. Moreover, when the data have large
uncertainties, more orbit integrations are necessary to explore each
data points uncertainty range. While it might be possible to speed up
the computation through linear approximations for nearby orbits, the
action--angle formalism allows for significant and elegant
simplifications and I consider the real--space approach further.

@@

\begin{figure}[t!]
  \includegraphics[width=0.5\textwidth,clip=]{gd1_evol_xz.ps}
  \caption{Mock tidal stream simulated as described in
    \sectionname~\ref{sec:sim} after $5.01\Gyr$ of evolution in
    Galactocentric $X$ and $Z$ coordinates. The grey dot shows the
    current position of the progenitor cluster and the dashed line
    shows its orbit. The solid line gives the stream track, calculated
    using the method described in \sectionname~\ref{sec:track}. The
    inset shows a zoomed-in version of part of the leading stream that
    more clearly shows the offset between the stream track and the
    progenitor orbit.}\label{fig:gd1_xz}
%python plot_stream.py ../tex/gd1_evol_xz.ps
\end{figure}

\begin{figure}[t!]
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aajrjz.ps}
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aaoroz.ps}
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aaaraz.ps}\\
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aajrjp.ps}
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aaorop.ps}
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aaarap.ps}
  \caption{Simulated tidal stream from \sectionname~\ref{sec:sim}
    after $5.01\Gyr$ of evolution in action--frequency--angle
    coordinates. The top row displays projections of the actions
    (left), frequencies (middle), and angles (right) in the $R$ and
    $Z$ directions; the bottom panels shows the same for $R$ and
    $\phi$. While the action distribution has a quite complicated
    form, the frequency distribution is close to one-dimensional and
    the leading and trailing parts of the stream clearly separate. In
    the right panels, the angles of the progenitor have each been
    shifted to $\pi$ and the dashed lines show the direction of the
    progenitor's frequency vector. The misalignment between the
    progenitor's frequency vector and the mean frequency vector of the
    debris is $0.18^\circ$.}\label{fig:gd1_jt}
%python plot_stream.py ../tex/gd1_evol_aajrjz.ps
%python plot_stream.py ../tex/gd1_evol_aaoroz.ps
%python plot_stream.py ../tex/gd1_evol_aaaraz.ps
%python plot_stream.py ../tex/gd1_evol_aajrjp.ps
%python plot_stream.py ../tex/gd1_evol_aaorop.ps
%python plot_stream.py ../tex/gd1_evol_aaarap.ps
\end{figure}

@@

\begin{figure}[t!]
  \includegraphics[width=\textwidth,clip=]{gd1_evol_lb.ps}
  \includegraphics[width=\textwidth,clip=]{gd1_evol_ld.ps}
  \caption{Simulated stream after $5.01\Gyr$ as a function of Galactic
    longitude. The top panel shows the stream in Galactic latitude and
    the bottom panel shows the distance from the Sun. The progenitor
    is shown as the large gray dot and its orbit as the dashed
    lines. The predicted track of the stream is shown as the solid
    line. Insets show various zoomed-in parts of the stream to show
    the stream, progenitor orbit, and predicted stream track up
    close.}\label{fig:gd1_lbd}
%python plot_stream.py ../tex/gd1_evol_lb.ps
%python plot_stream.py ../tex/gd1_evol_ld.ps
\end{figure}
\begin{figure}[t!]
  \includegraphics[width=\textwidth,clip=]{gd1_evol_lvlos.ps}
  \includegraphics[width=\textwidth,clip=]{gd1_evol_lpmll.ps}
  \includegraphics[width=\textwidth,clip=]{gd1_evol_lpmbb.ps}
  \caption{Simulated stream velocities as a function of Galactic
    longitude. Same as \figurename~\ref{fig:gd1_lbd}, but for the
    stream in heliocentric line-of-sight velocity $V_{\mathrm{los}}$
    (top panel), proper motion in the direction of Galactic longitude
    (middle panel), and in the direction of Galactic latitude (bottom
    panel). Insets again show various interesting parts of the stream
    up close.}\label{fig:gd1_lbv}
%python plot_stream.py ../tex/gd1_evol_lvlos.ps
%python plot_stream.py ../tex/gd1_evol_lpmll.ps
%python plot_stream.py ../tex/gd1_evol_lpmbb.ps
\end{figure}

>>>>

I illustrate the theoretical considerations set forth in this paper by
using a simulated tidal stream. This stream is set up similarly to
that used in \citet{Sanders13b}. The stream is constructed by running
an $N$-body simulation of a King cluster on an orbit similar to that
of the GD-1 stream \citep{Koposov10a}. Specifically, a King cluster
with a mass of $2\times10^4\msun$, a tidal radius of $0.07\kpc$, and a
ratio of the central potential to the velocity dispersion squared of
$2.0$ is sampled using $10^4$ particles. The cluster is evolved in an
external logarithmic host potential with $V_c = 220\kms$ and a
flattening $q=0.9$ ($\Phi = V_c^2 \ln [R^2 + z^2/q^2]$) using the
gyrfalcon code \citep{Dehnen00a,Dehnen02a} with a softening of
$1.5\pc$ in the NEMO toolkit \citep{Teuben95a}. The cluster is evolved
for $5.011\Gyr$ ($=5.125\kpc/[\kms]$) from the initial condition
$(X,Y,Z) = (-11.63337239,-20.76235661,-10.631736273934635)\kpc$ and
$(V_X,V_Y,V_Z) = (-128.8281653,42.88727925,79.172383882274971)\kms$,
chosen such that the cluster ends up at roughly the observed location
of the GD-1 stream at the end of the simulation
\citep{Koposov10a}. The progenitor's orbit has an eccentricity of
$0.31$, a pericenter of $13.7\kpc$, a current $r=14.4\kpc$, such that
the cluster is close to pericenter at the end of the simulation. The
actions of the progenitor are $(J_R,L_Z,J_Z) =
(288.5,-3173.7,897.6)\kpc\kms$ and its orbital frequencies are
$(\Omega_R,\Omega_\phi,\Omega_Z) = (15.7,-10.8,11.9)\Gyr\inv$.

@@

The action and frequency distributions shown in
\figurename~\ref{fig:gd1_jt} combined with the knowledge that for
\emph{any} tidal stream the Hessian $(\partial^2 H / \partial \vecj
\partial \vecj)\large|_{\vecj^p}$ must be strongly dominated by a
single large eigenvalue leads us to propose that frequency--angle
space is a better coordinate system than action--angle space for
modeling tidal streams. That is, the distribution of actions in a
tidal stream has a complicated structure that is hard to capture using
a simple, analytic form (see also the discussion in
\citealt{Eyre11a}). Especially the ``bowtie'' structure in $(J_R,L_Z)$
and the overlapping leading- and trailing-arm distributions in
($J_R,J_Z$) are hard to model with a simple distribution function. The
distribution of frequencies, however, is close-to one dimensional, its
direction of largest variance can be well-modeled as a Gaussian
(although below we will model it slightly differently), and its
parameters can all be easily estimated from the velocity dispersion of
the progenitor, the orbit of the progenitor, and the gravitational
potential, as discussed below. Therefore, we will model tidal streams
in frequency--angle space. Because the leading and trailing arm are
well-separated in frequency space, we model each arm individually.

@@

The distribution of frequencies is three dimensional. Because we model
the leading and the trailing arm separately, a single-peaked
distribution suffices to describe the frequency distribution. A
general description in terms of a Gaussian distribution would have
nine free parameters. However, we can model it with fewer free
parameters as follows. First, following \citet{Eyre11a}, we
approximate the \emph{action} distribution as a Gaussian with standard
deviations
\begin{equation}
  \sigma_{J_R} = \frac{1}{\pi}\,\sigv\,\left(r_{\mathrm{apo}}-r_{\mathrm{peri}}\right)\,,\quad 
  \sigma_{L_Z} = \sigv\,r_{\mathrm{peri}}\,,\quad 
  \sigma_{J_Z} = \frac{2}{\pi}\,\sigv\,Z_{\mathrm{max}}\,,
\end{equation}
where $\sigv$ is the velocity dispersion of the progenitor,
$r_{\mathrm{apo}}$ and $r_{\mathrm{peri}}$ are the apo- and pericenter
radii of the progenitor orbit, respectively, and $Z_{\mathrm{max}}$ is
the maximum $Z$ reached on this orbit. We assume that the all
correlations between the actions are zero (see
\figurename~\ref{fig:gd1_jt}). Then we propagate this Gaussian
variance to frequency space using the Hessian $(\partial^2 H /
\partial \vecj \partial \vecj)\large|_{\vecj^p}$\footnote{The Hessian
  $(\partial^2 H / \partial \vecj \partial \vecj)\large|_{\vecj^p}$
  can be computed using the method in \appendixname~\ref{sec:aa} by
  computing $\partial (\vecj,\veca) / \partial (\vecx,\vecv)$ and
  $\partial (\veco,\veca) / \partial (\vecx,\vecv)$ and forming
  $\partial \veco / \partial \vecj = \left(\partial (\vecj,\veca) /
  \partial (\vecx,\vecv)\right)^{-1}\,\left(\partial (\veco,\veca) /
  \partial (\vecx,\vecv)\right)$.}, which gives the variance matrix
$V_\veco$. The principal eigenvector of this matrix is the model
direction along which the stream spreads. While the model I propose
here is a simple one, it works well without having been tweaked for
the simulation under scrutiny. The angle between the principal
eigenvector of $V_\veco$ and the progenitor's frequency vector is
$0.50^\circ$ while the value measured from the simulation is
$0.18^\circ$. For a model with an isotropic action distribution, the
misalignment would be $1.28^circ$.

We then further constrain the mean frequency offset to lie along the
principal eigenvector of $V_\veco$. This mean frequency offset can be
described in terms of a parameter $\mu_\Omega = \Delta \Omega^m /
\sigma_{\Omega,1}$, where $\sigma_{\Omega,1}$ is the square root of
the largest eigenvalue of $V_\veco$ and $\Delta \Omega^m$ is the mean
frequency offset. The sign of this parameter sets whether we are
modeling a leading or a trailing arm. \figurename~\ref{fig:gd1_dohist}
shows the distribution frequency offsets in the direction of the
median frequency offset in the stream. The dashed line is a Gaussian
fit to this distribution, while the solid line is a fit of the form
\begin{equation}\label{eq:do}
  p(|\Delta \veco|_\parallel) = |\Delta \veco|_\parallel\,\mathcal{N}\left(|\Delta \veco|_\parallel|\Delta \Omega^m,\sigma_{\Omega,1}^2\right)\,,
\end{equation}
where $\mathcal{N}(\cdot|\cdot,\cdot)$ represents a Gaussian
distribution. The fit is equally good (because the dispersion is much
smaller than the mean) and we choose the second form because it
simplifies some of the stream-track calculations below. The best-fit
$(\Delta \Omega^m,\sigma_{\Omega,1})$ is $(0.19,0.033)\Gyr\inv$ in
both cases. Based on this information, a model with $\sigv =
0.365\kms$ and $\mu_\Omega = 6$ provides a good fit to the simulation
data. The distribution of frequency offsets in the two-dimensional
space perpendicular to the principal eigenvector of $V_\veco$ is
modeled as a zero-mean Gaussian with variance matrix given by the
projection of $V_\veco$ onto this space.

@@

@@

\begin{figure}[t!]
  \includegraphics[width=0.5\textwidth,clip=]{gd1_evol_xz.ps}
  \caption{Mock tidal stream simulated as described in
    \sectionname~\ref{sec:sim} after $5.011\Gyr$ of evolution in
    Galactocentric $X$ and $Z$ coordinates. The grey dot shows the
    current position of the progenitor cluster and the dashed line
    shows its orbit. The solid line gives the stream track, calculated
    using the method described in \sectionname~\ref{sec:track}. The
    inset shows a zoomed-in version of part of the leading stream that
    more clearly shows the offset between the stream track and the
    progenitor orbit.}\label{fig:gd1_xz}
%python plot_stream.py ../tex/gd1_evol_xz.ps
\end{figure}

\begin{figure}[t!]
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aajrjz.ps}
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aaoroz.ps}
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aaaraz.ps}\\
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aajrjp.ps}
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aaorop.ps}
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aaarap.ps}
  \caption{Simulated tidal stream from \sectionname~\ref{sec:sim}
    after $5.011\Gyr$ of evolution in action--frequency--angle
    coordinates. The top row displays projections of the actions
    (left), frequencies (middle), and angles (right) in the $R$ and
    $Z$ directions; the bottom panels shows the same for $R$ and
    $\phi$. While the action distribution has a quite complicated
    form, the frequency distribution is close to one-dimensional and
    the leading and trailing parts of the stream clearly separate. In
    the right panels, the angles of the progenitor have each been
    shifted to $\pi$ and the dashed lines show the direction of the
    progenitor's frequency vector. The misalignment between the
    progenitor's frequency vector and the mean frequency vector of the
    debris is $0.18^\circ$.}\label{fig:gd1_jt}
%python plot_stream.py ../tex/gd1_evol_aajrjz.ps
%python plot_stream.py ../tex/gd1_evol_aaoroz.ps
%python plot_stream.py ../tex/gd1_evol_aaaraz.ps
%python plot_stream.py ../tex/gd1_evol_aajrjp.ps
%python plot_stream.py ../tex/gd1_evol_aaorop.ps
%python plot_stream.py ../tex/gd1_evol_aaarap.ps
\end{figure}

@@

\begin{figure}[t!]
  \includegraphics[width=\textwidth,clip=]{gd1_evol_lb.ps}
  \includegraphics[width=\textwidth,clip=]{gd1_evol_ld.ps}
  \caption{Simulated stream after $5.011\Gyr$ as a function of Galactic
    longitude. The top panel shows the stream in Galactic latitude and
    the bottom panel shows the distance from the Sun. The progenitor
    is shown as the large gray dot and its orbit as the dashed
    lines. The predicted track of the stream is shown as the solid
    line. Insets show various zoomed-in parts of the stream to show
    the stream, progenitor orbit, and predicted stream track up
    close.}\label{fig:gd1_lbd}
%python plot_stream.py ../tex/gd1_evol_lb.ps
%python plot_stream.py ../tex/gd1_evol_ld.ps
\end{figure}
\begin{figure}[t!]
  \includegraphics[width=\textwidth,clip=]{gd1_evol_lvlos.ps}
  \includegraphics[width=\textwidth,clip=]{gd1_evol_lpmll.ps}
  \includegraphics[width=\textwidth,clip=]{gd1_evol_lpmbb.ps}
  \caption{Simulated stream velocities as a function of Galactic
    longitude. Same as \figurename~\ref{fig:gd1_lbd}, but for the
    stream in heliocentric line-of-sight velocity $V_{\mathrm{los}}$
    (top panel), proper motion in the direction of Galactic longitude
    (middle panel), and in the direction of Galactic latitude (bottom
    panel). Insets again show various interesting parts of the stream
    up close.}\label{fig:gd1_lbv}
%python plot_stream.py ../tex/gd1_evol_lvlos.ps
%python plot_stream.py ../tex/gd1_evol_lpmll.ps
%python plot_stream.py ../tex/gd1_evol_lpmbb.ps
\end{figure}
